DisjunctiveProgramming.jl: Generalized Disjunctive Programming Models and Algorithms for JuMP

### 2022-10-11 paper/paper.tex
add note to CNF conversion

Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence,

>>>>

Once the logic propositions are converted to CNF, each clause can be converted into an algebraic constraint with the following equivalence (Note: any negated Boolean variables, $\neg Y_i$, are replaced with $1-y_i$ in the reformulation),
